Blocking-resistant communication\\through domain fronting

### 2014-07-16 docs/meek.tex
Note to note GoAgent's non-workingness.
Some more on active probing.

Broadly speaking, there are two main challenges to proxy-based circumvention:
blocking by content and blocking by address.
Blocking by content is based on \emph{what you are saying},
and blocking by address is based on \emph{whom you are speaking to},
A skilled censor will do both, and effective circumvention requires meeting both challenges.
A content-blocking censor inspects packets and payloads,
looking, for example, for forbidden protocols or keywords.
Content-based blocking is countered by obfuscation:
making circumvention traffic difficult to distinguish
from traffic the censor wishes to allow.
An address-blocking censor forbids all communication with certain
addresses, for example IP addresses and domain names, whatever the contents may be.
The challenge of address blocking is met by making it difficult for the censor to learn proxy addresses;
by having overwhelmingly many proxies;
or by colocating proxies with high-value services so that both must be blocked or both allowed.

To the above challenges we may add the related challenge of active scanning for proxies.
Though a circumvention protocol may be difficult to identify on the wire,
it may nevertheless be easy to scan for servers that speak the protocol,
and thereafter block the server by its address.
Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
by actively scanning destination addresses to see if they speak the Tor protocol.
The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit}
and in this work.

@@

>>>>

Broadly speaking, there are two main challenges to proxy-based circumvention:
blocking by content and blocking by address.
Blocking by content is based on \emph{what you are saying},
and blocking by address is based on \emph{whom you are speaking to},
A skilled censor will do both, and effective circumvention requires meeting both challenges.
A content-blocking censor inspects packets and payloads,
looking, for example, for forbidden protocols or keywords.
Content-based blocking is sometimes called deep packet inspection (DPI).
Content-based blocking is countered by obfuscation:
making circumvention traffic difficult to distinguish
from traffic the censor wishes to allow.
An address-blocking censor forbids all communication with certain
addresses, for example IP addresses and domain names, whatever the contents may be.
The challenge of address blocking is met by making it difficult for the censor to learn proxy addresses;
by having overwhelmingly many proxies;
or by colocating proxies with high-value services so that both must be blocked or both allowed.

To the above challenges we may add the related challenge of active probing.
An active-probing censor tries to connect to a server using a circumvention tool
as if it were an ordinary client.
If the connection is successful, the server can be blacklisted.
Active probing is a very precise means of identifying a server as belonging to a circumvention system.
Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
by issuing followup scans to observed client connections to see
whether a server speaks the Tor protocol.
The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit}
and in this work.

@@

% GoAgent not working since June 2014.
